### 2019-05-14 Paper/paper.tex
added current iteration of the paper

\documentclass[journal=jpcafh,manuscript=article]{achemso}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{natbib}

\SectionNumbersOn

\author{Franz Martinez}
\email{franzmichel.martinez@ucalgary.ca}
\affiliation{Schulich School of Engineering, University of Calgary, Calgary, Alberta, Canada}
\title{Outline--Draft JCP format for: Reactive Force Field for Perovskite--Based Solid Oxides and Its Application to Solid Oxide Electrolysis Cells}

\begin{document}

\begin{abstract}
Conversion of CO2 to syngas can be achieved in solid oxide electrolysis cells at high temperatures (~1000 K) by using Perovskite-based solid oxides as electrocatalysts. This process is projected to be a viable way of generating fuels by converting, and therefore reducing, CO2 from industrial emissions. However, full understanding of the mechanism involved in CO2 conversion on these electrocatalysts is far from complete. In this work, we perform DFT calculations and reactive molecular dynamics to understand the electronic structure and stability of perovskite-based solid oxides used as electrocatalysts for CO2 conversion. To this end, our study involves firstly, generation of a dataset from DFT calculations, which include optimized geometries, equations of state, surface energies, and slab—CO2 interactions from a set of ABO3-type perovskites. Secondly, we parametrize the reactive force field, ReaxFF, using an annealing Monte Carlo optimizer and a covariance matrix adaptation evolution strategy. Finally, we explore bulk dynamics of the perovskites at high temperature and the time evolution of reactions involving CO2 on the surface of slabs from the perovskites. Of interest, our results demonstrate the modes in which the CO2 is chemisorbed at high temperature; the consequent formation of intermediates; and their role in further conversion of the CO2. This study serves as a base to elucidate the elementary steps involved in the mechanism of CO2 conversion on perovskites at high temperature, which will allow us to understand the most favorable conditions for the reaction to occur and, consequently, provide us of a way to improve the design of perovskite-based solid oxide electrocatalysts.
\end{abstract}

\section{Introduction}

CO$_2$, electrocatalysts, and solid oxide fuels.\cite{
habisreutinger_photocatalytic_2013,
e.benson_electrocatalytic_2009,
pradeepindrakanti_photoinduced_2009,
indrakanti_quantum_2009,
zeng_review_2018,
yamada_systematic_2018,
kar_enhanced_2016,
grimaud_double_2013,
ni_electrochemical_2012,
tan_co_2011,
baniecki_photoemission_2008,
jia_heterogeneous_2017,
yin_oxide_2018,
zheng_review_2017,
andersson_review_2010,
beatriz_microwave-assisted_2015}

DFT studies.\cite{tian_dft_2018,
mayeshiba_strain_2017,
wang_oxidation_2006,
li_density_2013,
liu_influence_2018,
seo_design_2015,
evarestov_adsorption_2007,
pilania_establishing_2012,
pilania_adsorption_2010,
zurek_predicting_2015}

Molecular dynamics studies.\cite{wang_coarse-grained_2014}

\section{Computational Methods}

\subsection{ReaxFF and Parameterization Strategy}

ReaxFF is a force field based on the dynamical computation of the bond-order, which dictates the connectivity between atoms on the fly.
This approach allows ReaxFF to consider bond breaking and formation, and therefore the ability to follow the apparition of intermediates involved in the reaction mechanism in complex systems containing thousands of atoms.\cite{migliorati_development_2017,merinov_reaxff_2014,
raymand_reactive_2008,
shin_development_2015,
van_duin_reaxff_2008,
goddard_development_2006,
hubin_parameterization_2016,
senftle_reaxff_2016,
chenoweth_reaxff_2009,
chenoweth_reaxff_2008,
van_duin_reaxff_2008-1,
liu_reaxff-lg:_2011}

Its use bridges the advantages of classical molecular dynamics simulation with those of quantum--mechanical approaches.

Parametrization of ReaxFF involves generation of a dataset, generally from quantum mechanical calculations, and subsequent fitting of the force field parameters with respect to the dataset by minimizing the error function, $E_f$,
\begin{equation}
E_f = \frac{(x_{i} - x_{ReaxFF,i})^2}{w_i}.
\end{equation}
Where $x_{i}$ is the value of a property $x$ (e.g. heat of formation, geometries, energetic differences, etc.); $x_{ReaxFF,i}$ is such property calculated using ReaxFF; and $w_i$ is the weight, or accuracy, associated to the desired deviation between both $x_i$ and $x_{ReaxFF,i}$
In this work the Monte Carlo Force Field Optimizer,\cite{iype_parameterization_2013} part of the ADF package, has been used to fit the various parameters of the force field, mostly because the method has been shown to give good results independent of the initial guess for the force fields parameters.

The parametrization of the force field was performed using various stages, and it started with known parameters for C, H, O, S, Fe, and Cr from a previous study of hydrocarbon oxidation on pyrite--covered Cr$_2$O$_3$; \cite{shin_development_2015} and for Ca from a previous study of calcium oxyde hydration. \cite{manzano_hydration_2012}

With starting parameters for most elements except for La, the first stage of the parametrization involved fitting the La--La parameters of the force field to the following: quantum mechanically calculated equations of state corresponding to three solid phases of La, i.e. double hexagonal close packed (dhcp, $\alpha$-La), face centered cubic (fcc, $\gamma$-La), and body centered cubic (bcc, $\beta$-La); and data from the electronic structure calculation of the La$_2$ molecule was added.
This stage was carried out while keeping parameters for other interactions unchanged.
The following stage involved further fitting of the La--La parameters, namely those related to the electrostatic interaction (EEM shielding, EEM electronegativity, and EMM hardness), and the La--O parameters by adding to the dataset Mulliken charges and geometrical information obtained from the optimized structures of the La$_2$O$_3$ cluster, three La$_4$O$_6$ clusters, and one La$_6$O$_9$ cluster.
Also, the equations of state corresponding to two solid structures of La$_2$O$_3$ were computed and added.

\subsection{Electronic Structure Calculations for Dataset Generation}

DFT calculations are carried out using Quantum Espresso,\cite{giannozzi_advanced_2017} for all solid oxides in bulk or slab form.
Calculations were performed using the pseudo--potentials from the PSlibrary with scalar-relativistic effects due to the presence of Lanthanum \textbf{put references}.
A value of 75.0 Ry was used for the kinetic energy cutoff, which were tested for convergence ensuring that $\Delta E_{tot} / \Delta E_{cut} <$ 0.01 eV per atom.
Monkhorst-Pack k-point sampling of the Brillouin zone was chosen to be $4\times4\times4$ for most calculations using cells of approximately 5.5 \AA $\times$ 7.6 \AA $\times$ 5.5 \AA, due to the variable size of the cells after variable cell relaxation.
The k-point grid used was also tested using the same criterion to ensure convergence.

Because the transition metals present localized electronic density on their d--orbitals with strong correlation, the Hubbard correction is employed to take into account these effects.\textbf{put references}
Values used for the Hubbard term, U, were taken from \textbf{put values, and justify about not determining their values from linear response theory}

The convergence criterion used for all calculations was of 0.02 eV for the total energy, and in the case of relaxations the maximum force component on each atom had to satisfy being smaller than 0.01 eV/\AA

Some energetic and geometric parameters were also obtained from clusters and molecules in the gas phase using the ADF package.
Here, for consistency with other parameters obtained previously for ReaxFF, the B3LYP functional has been used with TZP STO--basis functions.
Scalar relativistic effects were introduced using the ZORA correction.

\subsection{Molecular Dynamics Trajectories Using ReaxFF}

For the molecular dynamics simulations using ReaxFF, the system \textbf{specify details for bulk simulations and slabs} ... first is equilibrated using classical molecular dynamics with the UFF force field.
From the equilibrated trajectory at the conditions required \textbf{double check temperature and pressure and change this part}, several points are selected randomly as starting points for the simulation.
This ensures that the system starts from a correct point in equilibrium of the ensemble for the ReaxFF dynamics.

\section{Results and Discussion}

\subsection{Equations of State}

Equations of state for hexagonal La, LaFeO$_3$, LaCrO$_3$, ... were calculated using DFT, and the ReaxFF force field was parametrized to reproduce this curve to the best possible fit.
Because the relationship between energy and volume in solids allow to capture the stability of the phase, fitting of these curves give ReaxFF the ability to model accurately the bulk phase of the perovskite.

The bulk modulus for $\alpha$-La was obtained by fitting the calculated points to the Birch-Murnaghan equation of state\cite{fu_first-principles_1983}, and the value obtained of 25.6\,GPa agrees with an approximate 8\% of error compared to the reported experimental bulk modulus value of 27.9\,GPa.\cite{lide2003crc}

\subsection{Surface Energies}

Given the differences, in structure and energetics, of the surface compared to the bulk, it is necessary to introduce this behaviour to the force field.
To this end, slabs of various perovskites were constructed from their bulk counterparts to extend the ReaxFF force field.
\textbf{Calculations currently going on}

\subsection{Oxygen Vacancy Formation Energies}

Introduction of Ca and Sr in the A--site of the perovskites favours the formation of oxygen vacancies due to the change in ionic size compared to La and the different charges of these cations. \textbf{cite}
Also, this changes allows for oxygen ionic diffusion through the solid.
The existence of oxygen vacancies in the system needs to be captured by ReaxFF in the form of correctly capturing changes in the chemical environment and in the relative stability of the perovskite unit cell in the absence of one oxygen.
For various perovskites, the oxygen vacancy formation energy is calculated and incorporated into the dataset used to fit ReaxFF.

\section{Applications and Discussion}

\subsection{Oxygen Diffusion through the Perovskites}

To exemplify the dynamics on the bulk, diffusion of O$_2^{-2}$ is followed through the perovskite in bulk phase.

Also, to account for the accuracy of the force field, the expansion coefficient is computed for LCFCr and LSFCr.
This value is compared to experimental results ...

\subsection{CO$_2$ Interactions on the Surface}

Using a slab of a representative portion \textbf{fill in details of the real size} of the surface of the LCFCr, various mixtures of gases are fed into one of the surfaces ...

Formation of intermediates is observed at 1073 K \textbf{double check temperature}

\section{Concluding Remarks}

\begin{acknowledgement}
This work has been enabled by the use of computing resources provided by Compute Canada.
\end{acknowledgement}

\pagebreak

\bibliography{co2perov2}

\pagebreak
\begin{tocentry}
\begin{center}
%\includegraphics{toc.eps}
insert ToC if requested
\end{center}
\end{tocentry}

\end{document}

### 2019-05-14 Paper/paper.tex
Reworded paragraph of DFT methods

@@
 
-DFT calculations are carried out using Quantum Espresso,\cite{giannozzi_advanced_2017} for all solid oxides in bulk or slab form.
-Calculations were performed using the pseudo--potentials from the PSlibrary with scalar-relativistic effects due to the presence of Lanthanum \textbf{put references}.
-A value of 75.0 Ry was used for the kinetic energy cutoff, which were tested for convergence ensuring that $\Delta E_{tot} / \Delta E_{cut} <$ 0.01 eV per atom.
-Monkhorst-Pack k-point sampling of the Brillouin zone was chosen to be $4\times4\times4$ for most calculations using cells of approximately 5.5 \AA $\times$ 7.6 \AA $\times$ 5.5 \AA, due to the variable size of the cells after variable cell relaxation.
-The k-point grid used was also tested using the same criterion to ensure convergence.
+DFT calculations are carried out using Quantum Espresso,\cite{giannozzi_advanced_2017} for all solid structures in bulk or slab form.
+These calculations were performed using the pseudo--potentials from the PSlibrary including scalar-relativistic effects due to the presence of Lanthanum \textbf{put references}.
+A value of 75.0 Ry was used for the kinetic energy cutoff, which was tested for convergence ensuring that $\Delta E_{tot} / \Delta E_{cut} <$ 0.01 eV was obtained per atom.
+Monkhorst-Pack k-point sampling of the Brillouin zone was chosen to be $4\times4\times4$ for most calculations.
+The criterion used involved using a k-point grid of 4 on the edge of a cell between 5 and 8 \AA in length, then to preserve the grid on bigger or smaller cells, the grid was scaled accordingly.
+The k-point grids used were also tested using the same criterion from energy converge to ensure convergence with respect to grid size.
 

### 2019-05-16 Paper/paper.tex

@@
 
-Some energetic and geometric parameters were also obtained from clusters and molecules in the gas phase using the ADF package.
-Here, for consistency with other parameters obtained previously for ReaxFF, the B3LYP functional has been used with TZP STO--basis functions.
-Scalar relativistic effects were introduced using the ZORA correction.
+Differences in energies and optimized geometries were also obtained from clusters in the gas phase using \emph{Gaussian16} \textbf{put references}.
+For these calculations, the B3LYP functional has been used with the aug--cc--pVTZ basis functions for oxygen and for lanthanum the La basis set from the Stuttgart/Dresden group, La(RSC97) \textbf{double check} with a 28--electron ECP \textbf{citation}.
+By using this approach, we ensure that the parameters obtained for lanthanum in these calculations are consistent with the way the oxygen parameters were obtained in previous studies.
 

### 2019-05-17 Paper/paper.tex
Update paper.tex

@@
 \section{Introduction}
+
+% introduce lanthanum uses
+Lanthanum is an element involved either as a catalyst or as a ion in supporting structures of other active catalytic materials.
+Particularly, catalysts based on a form of Lanthanum oxide have shown a good efficiency in the oxidative coupling of methane to form ethane and/or ethylene \textbf{import citation}, or as main components of electro--catalysts used in CO$_2$ conversion to CO \textbf{import citation}.
+
+% what is the problem with lanthanum
+
+Given the importance of this element in its applications, quantum mechanical calculations have been carried out to understand its role and influence, if any, on the systems where it is found.
+However, many of the phenomena that takes place in catalysis involve the interaction of a
 

### 2019-05-17 Paper/paper.tex
References added
Three references used in introduction

--- 2019-05-16 Paper/paper.tex
@@
 
+% introduce lanthanum uses
+Lanthanum is a transition metal involved in various applications that range from use in catalysts, batteries, and in medicine \cite{atwood2013rare,he2013preparation}.
+Particularly, catalysts based on Lanthanum oxide have shown a good efficiency in the oxidative coupling of methane to form ethane and/or ethylene \textbf{import citation}, or as main components of electro--catalysts used in CO$_2$ conversion to CO \textbf{import citation}.
+
+% what is the problem with lanthanum
+\emph{need to introduce more about uses of La}
+
+Quantum mechanical calculations have been carried out to understand the role and influence, if any, of Lanthanum on its many applications.
+However, many of the phenomena that takes place in catalysis involve the interaction of many atoms for which rigorous quantum mechanical calculations are unfeasible.
+For this reason, force fields are commonly used to study applications via molecular dynamics calculations.
+In particular, the behaviour of La$^3+$ in aqueous solution has been studied by various groups using different parametrization strategies to improve the accuracy of the description of the interaction between Lanthanum and water \cite{duvail2007pair}.
+These approaches have proven to successfully describe the La--O interaction in liquid water, but due to the size of Lanthanum the introduction of some form of explicit polarizability is necessary to properly describe the interactions between Lanthanum and other elements.
+
+One of the major drawbacks of the use of general polarizable force fields is the impossibility to describe chemical reactions, as these models disable explicit bond breaking and formation to produce transferable parameters and simple expressions for calculating energies and forces.
+But, with the increasing computational power processing, reactive force fields that can capture bond breaking and formation on--the--fly have been developed actively during the last decade.
+Particularly, ReaxFF is a reactive force field that has been extensively used to study successfully reactive events between solid, liquid, and gas phases.
+This transferability between phases, and the possibility to study phenomena where chemical events and dynamical factors are of importance makes ReaxFF a powerful tool that bridges the lower computational expense from force fields and the quantum mechanical description of a system.
+Although the current form of ReaxFF has been in development since 2008 \cite{chenoweth_reaxff_2008} and many elements have been parametrized to be used in ReaxFF not all interactions have been fully parametrized, and some elements still remain to be parametrized.
+An important point is that parameters used in ReaxFF are heavily dependent on the applications for which they have been explicitly parametrized, so while some parameters can be transferable testing is necessary to ensure that interactions are well described.
+
+The purpose of this study is to generate a set of parameters for Lanthanum as well as its interaction with other elements, namely Ca, Fe, Cr, and O, to be used for describing solid state materials used in catalysis.
+To this end, in the remainder of this paper, we introduce ReaxFF and a parametrization strategy in Sec.~\ref{sec:reaxff-strategy}; and the computational methods used, i.e.
+electronic structure calculations in Sec.~\ref{sec:dft-details}; and molecular dynamics simulations in Sec.~\ref{sec:md-details}.
+Then, we discuss in Sec.~\ref{sec:results-and-discussion} the quality of the newly generated parameters by analyzing the ability of the ReaxFF to reproduce the generated dataset from quantum mechanical calculations.
+Finally, we use the parameters obtained to model some possible applications discuss the results in Sec.~\ref{sec:applications}, and present our concluding remarks in Sec.~\ref{sec:conclusions}
+
 CO$_2$, electrocatalysts, and solid oxide fuels.\cite{
@@
 \subsection{ReaxFF and Parameterization Strategy}
+\label{sec:reaxff-strategy}
 
@@
 \subsection{Electronic Structure Calculations for Dataset Generation}
+\label{sec:dft-details}
 
@@
 \subsection{Molecular Dynamics Trajectories Using ReaxFF}
+\label{sec:md-details}
 
@@
 
-\section{Results and Discussion}
+\section{Parametrization Results and Discussion}
+\label{sec:results-and-discussion}
 
@@
 
-\section{Applications and Discussion}
+\section{Applications}
+\label{sec:applications}
 
@@
 \section{Concluding Remarks}
+\label{sec:conclusions}
 

### 2019-05-17 Paper/paper.tex
Update paper.tex
After updating introduction, commented references that I may end up not using.

@@
 
-CO$_2$, electrocatalysts, and solid oxide fuels.\cite{
-habisreutinger_photocatalytic_2013,
-e.benson_electrocatalytic_2009,
-pradeepindrakanti_photoinduced_2009,
-indrakanti_quantum_2009,
-zeng_review_2018,
-yamada_systematic_2018,
-kar_enhanced_2016,
-grimaud_double_2013,
-ni_electrochemical_2012,
-tan_co_2011,
-baniecki_photoemission_2008,
-jia_heterogeneous_2017,
-yin_oxide_2018,
-zheng_review_2017,
-andersson_review_2010,
-beatriz_microwave-assisted_2015}
-
-DFT studies.\cite{tian_dft_2018,
-mayeshiba_strain_2017,
-wang_oxidation_2006,
-li_density_2013,
-liu_influence_2018,
-seo_design_2015,
-evarestov_adsorption_2007,
-pilania_establishing_2012,
-pilania_adsorption_2010,
-zurek_predicting_2015}
-
-Molecular dynamics studies.\cite{wang_coarse-grained_2014}
+%CO$_2$, electrocatalysts, and solid oxide fuels.\cite{
+%habisreutinger_photocatalytic_2013,
+%e.benson_electrocatalytic_2009,
+%pradeepindrakanti_photoinduced_2009,
+%indrakanti_quantum_2009,
+%zeng_review_2018,
+%yamada_systematic_2018,
+%kar_enhanced_2016,
+%grimaud_double_2013,
+%ni_electrochemical_2012,
+%tan_co_2011,
+%baniecki_photoemission_2008,
+%jia_heterogeneous_2017,
+%yin_oxide_2018,
+%zheng_review_2017,
+%andersson_review_2010,
+%beatriz_microwave-assisted_2015}
+%
+%DFT studies.\cite{tian_dft_2018,
+%mayeshiba_strain_2017,
+%wang_oxidation_2006,
+%li_density_2013,
+%liu_influence_2018,
+%seo_design_2015,
+%evarestov_adsorption_2007,
+%pilania_establishing_2012,
+%pilania_adsorption_2010,
+%zurek_predicting_2015}
+%
+%Molecular dynamics studies.\cite{wang_coarse-grained_2014}
 

### 2019-05-17 Paper/paper.tex
updated paper.tex and removed previous draft

@@
 \affiliation{Schulich School of Engineering, University of Calgary, Calgary, Alberta, Canada}
-\title{Outline--Draft JCP format for: Reactive Force Field for Perovskite--Based Solid Oxides and Its Application to Solid Oxide Electrolysis Cells}
+\title{Outline--Draft JCP format for: Reactive Force Field for Solid Oxides Containing Lanthanum}
 
@@
 \begin{abstract}
+\textbf{abstract needs to be updated}
+
 Conversion of CO2 to syngas can be achieved in solid oxide electrolysis cells at high temperatures (~1000 K) by using Perovskite-based solid oxides as electrocatalysts.
@@
 
-Introduction of Ca and Sr in the A--site of the perovskites favours the formation of oxygen vacancies due to the change in ionic size compared to La and the different charges of these cations.
-\textbf{cite}
-Also, this changes allows for oxygen ionic diffusion through the solid.
-The existence of oxygen vacancies in the system needs to be captured by ReaxFF in the form of correctly capturing changes in the chemical environment and in the relative stability of the perovskite unit cell in the absence of one oxygen.
+Introduction of Ca in the A--site of the perovskites favours the formation of oxygen vacancies due to the change in ionic size compared to La and the different charges of these cations. \textbf{cite}
+Also, the formation of oxygen vacancies allow for ionic diffusion through the solid, which is an important process present when these solids are used as electrodes in solid oxide fuel or electrolysis cells.
+The existence of oxygen vacancies in the system needs to be captured by ReaxFF in the form of correctly capturing changes in the chemical environment and in the relative stability of the solid unit cell in the absence of one oxygen.
 For various perovskites, the oxygen vacancy formation energy is calculated and incorporated into the dataset used to fit ReaxFF.
@@
 
+\subsection{Nanoparticle formation of La$_2$O$_3$}
+
 \subsection{Oxygen Diffusion through the Perovskites}
@@
 To exemplify the dynamics on the bulk, diffusion of O$_2^{-2}$ is followed through the perovskite in bulk phase.
-
-Also, to account for the accuracy of the force field, the expansion coefficient is computed for LCFCr and LSFCr.
-This value is compared to experimental results ...
+Also, to account for the accuracy of the force field, the expansion coefficient is computed for LCFCr and this value is compared to experimental results.
 
 \subsection{CO$_2$ Interactions on the Surface}
+
+\textbf{this may be ommited for a future paper}
 

### 2019-05-24 Paper/paper.tex
Update paper.tex
Cleaned up some lines
Updated abstract
Changed abstract to be more in line with intended study of La

@@
 
-Conversion of CO2 to syngas can be achieved in solid oxide electrolysis cells at high temperatures (~1000 K) by using Perovskite-based solid oxides as electrocatalysts.
-This process is projected to be a viable way of generating fuels by converting, and therefore reducing, CO2 from industrial emissions.
-However, full understanding of the mechanism involved in CO2 conversion on these electrocatalysts is far from complete.
-In this work, we perform DFT calculations and reactive molecular dynamics to understand the electronic structure and stability of perovskite-based solid oxides used as electrocatalysts for CO2 conversion.
-To this end, our study involves firstly, generation of a dataset from DFT calculations, which include optimized geometries, equations of state, surface energies, and slab—CO2 interactions from a set of ABO3-type perovskites.
-Secondly, we parametrize the reactive force field, ReaxFF, using an annealing Monte Carlo optimizer and a covariance matrix adaptation evolution strategy.
-Finally, we explore bulk dynamics of the perovskites at high temperature and the time evolution of reactions involving CO2 on the surface of slabs from the perovskites.
-Of interest, our results demonstrate the modes in which the CO2 is chemisorbed at high temperature; the consequent formation of intermediates; and their role in further conversion of the CO2.
-This study serves as a base to elucidate the elementary steps involved in the mechanism of CO2 conversion on perovskites at high temperature, which will allow us to understand the most favorable conditions for the reaction to occur and, consequently, provide us of a way to improve the design of perovskite-based solid oxide electrocatalysts.
+In this work, we perform the parametrization of a reactive force field, ReaxFF, for Lanthanum and its oxides.
+We describe the procedure followed and provide results that validate the derived parameters in their ability to describe bulk structures, surfaces, and nanoparticles.
+Comparison of our results using ReaxFF and electronic structure methods show good agreement in the reproduction of surfaces energies and bulk modulus; with the latter showing good agreement with experimentally reported results.
+We also show that our parametrization is able to capture the trend in adsorption energies between Lanthanum oxides and adsorbates like methane and water \textbf{to be obtained}.
+These results highlight the utility of ReaxFF to study systems containing Lanthanum and provide a significant addition to reactive molecular dynamics for studying properties and even redox properties on Lanthanum oxide surfaces.
+
 \end{abstract}

### 2019-06-01 Paper/paper.tex
Update paper.tex
Added La-EoS figure and discussion about it

@@
 \usepackage{natbib}
+
+\graphicspath{ {./images/} }
 
@@
 
+\begin{figure}[hbtp]
+\centering
+\includegraphics[scale=1]{three-La-eos.pdf}
+\caption{Calculated equations of state corresponding to crystalline La in hexagonal (top), fcc (middle), and bcc (bottom) forms.}
+\label{fig:laeos}
+\end{figure}
+
+The equations of state for the three forms of Lanthanum are presented in Fig.~\ref{fig:laeos}.
+The plots show the parabolic behaviour of the equation of state, and that the parametrized ReaxFF can reproduce the results from DFT within an acceptable margin of error.
+As for the trends in stability of the three phases, ReaxFF is unable to properly reproduce it.
+The reported experimental trend places $\alpha$-La as the most stable, followed by $\gamma$-La, and then by$\beta$-La.
+In the case of ReaxFF the trend goes from most stable to less stable as $\gamma$-La, $\beta$-La, and $\alpha$-La.
+While the inability to reproduce stability is a known issue in ReaxFF, it is worth mentioning that in the case of La, the differences in energy between the phases is in the order of $\approx$~0.5~kcal/mol.
+It is then unsurprising that the parametrized force field is unable to exactly reproduce the trend,  given how small the difference in energy is compared to the target error in the fitting of the force field, which averages around 5~kcal/mol.
+
 The bulk modulus for $\alpha$-La was obtained by fitting the calculated points to the Birch-Murnaghan equation of state\cite{fu_first-principles_1983}, and the value obtained of 25.6\,GPa agrees with an approximate 8\% of error compared to the reported experimental bulk modulus value of 27.9\,GPa.\cite{lide2003crc}

### 2019-06-11 Paper/paper.tex
Updated text, and moved images

@@
 \begin{abstract}
-\textbf{abstract needs to be updated}
+\textbf{abstract needs to be updated to reflect last changes}
 
@@
 
-With starting parameters for most elements except for La, the first stage of the parametrization involved fitting the La--La parameters of the force field to the following: quantum mechanically calculated equations of state corresponding to three solid phases of La, i.e.
+With starting parameters for most elements except for Lanthanum, the first stage of the parametrization involved fitting the La--La parameters of the force field to the following: quantum mechanically calculated equations of state corresponding to three solid phases of La, i.e.
 double hexagonal close packed (dhcp, $\alpha$-La), face centered cubic (fcc, $\gamma$-La), and body centered cubic (bcc, $\beta$-La); and data from the electronic structure calculation of the La$_2$ molecule was added.
@@
 Because the relationship between energy and volume in solids allow to capture the stability of the phase, fitting of these curves give ReaxFF the ability to model accurately the bulk phase of the perovskite.
-
-\begin{figure}[hbtp]
-\centering
-\includegraphics[scale=1]{three-La-eos.pdf}
-\caption{Calculated equations of state corresponding to crystalline La in hexagonal (top), fcc (middle), and bcc (bottom) forms.}
-\label{fig:laeos}
-\end{figure}
 
@@
 \begin{acknowledgement}
-This work has been enabled by the use of computing resources provided by Compute Canada.
+This work was supported by the Canada First Research Excellence Fund (CFREF) Global Research Initiative (GRI) in Sustainable Low Carbon Unconventional Resources.
+Computational work has been enabled by the use of computing resources provided by Compute Canada.
 \end{acknowledgement}
+
+\pagebreak
+
+\begin{figure}[hbtp]
+\centering
+\includegraphics[width=\textwidth]{three-La-eos.pdf}
+\caption{Calculated equations of state corresponding to crystalline La in hexagonal (top), fcc (middle), and bcc (bottom) forms.}
+\label{fig:laeos}
+\end{figure}
 

### 2019-06-13 Paper/paper.tex
Update paper.tex
Added default scale for image
Updates from Overleaf

@@
 ReaxFF is a force field based on the dynamical computation of the bond-order, which dictates the connectivity between atoms on the fly.
-This approach allows ReaxFF to consider bond breaking and formation, and therefore the ability to follow the apparition of intermediates involved in the reaction mechanism in complex systems containing thousands of atoms.\cite{migliorati_development_2017,merinov_reaxff_2014,
+This approach allows ReaxFF to consider bond breaking and formation, and therefore permits to follow the apparition of intermediates.
+In complex systems this ability proves to be invaluable for following reaction mechanism when the number of atoms are in the order of thousands or higher.\cite{migliorati_development_2017,merinov_reaxff_2014,
 raymand_reactive_2008,
@@
 liu_reaxff-lg:_2011}
-
-Its use bridges the advantages of classical molecular dynamics simulation with those of quantum--mechanical approaches.
+This way, ReaxFF bridges classical molecular dynamics and quantum--mechanical approaches while avoiding exponential scaling of calculation times.
 

### 2019-08-20 Paper/paper.tex
added two plots and info about La2O3

@@
 % introduce lanthanum uses
-Lanthanum is a transition metal involved in various applications that range from use in catalysts, batteries, and in medicine \cite{atwood2013rare,he2013preparation}.
+Lanthanum and Lanthanum oxide are materials involved in various applications involving catalysts, batteries, and medicine \cite{atwood2013rare,he2013preparation}.
 Particularly, catalysts based on Lanthanum oxide have shown a good efficiency in the oxidative coupling of methane to form ethane and/or ethylene \textbf{import citation}, or as main components of electro--catalysts used in CO$_2$ conversion to CO \textbf{import citation}.
@@
 
-The purpose of this study is to generate a set of parameters for Lanthanum as well as its interaction with other elements, namely Ca, Fe, Cr, and O, to be used for describing solid state materials used in catalysis.
-To this end, in the remainder of this paper, we introduce ReaxFF and a parametrization strategy in Sec.~\ref{sec:reaxff-strategy}; and the computational methods used, i.e.
+The purpose of this study is to generate a set of parameters for Lanthanum and Lanthanum Oxide that can be used for describing solid state materials used in catalysis and as a base for further development in applications that involve interactions with CO$_2$ or H$_2$O to name a couple.
+To this end, in the remainder of this paper, we introduce ReaxFF and a parametrization strategy in Sec.~\ref{sec:reaxff-strategy}; the computational methods used, i.e.
 electronic structure calculations in Sec.~\ref{sec:dft-details}; and molecular dynamics simulations in Sec.~\ref{sec:md-details}.
@@
 
-Equations of state for hexagonal La, LaFeO$_3$, LaCrO$_3$, ... were calculated using DFT, and the ReaxFF force field was parametrized to reproduce this curve to the best possible fit.
-Because the relationship between energy and volume in solids allow to capture the stability of the phase, fitting of these curves give ReaxFF the ability to model accurately the bulk phase of the perovskite.
+Equations of state for hexagonal La, ...
+La$_2$O$_3$, ...
+\emph{fill in other crystals} were calculated using DFT, and ReaxFF was parametrized to reproduce these curves to the best possible fit, i.e.
+using weights of 0.1 to 1.0.
+Because the relationship between energy and volume in solids allows to capture the stability of the phase, fitting of these curves give ReaxFF the ability to model accurately the bulk phase of the crystal structures for which it has been explicitly trained.
+
+\emph{all these results may actually change as the force field gets improved}
 
 The equations of state for the three forms of Lanthanum are presented in Fig.~\ref{fig:laeos}.
-The plots show the parabolic behaviour of the equation of state, and that the parametrized ReaxFF can reproduce the results from DFT within an acceptable margin of error.
+The plots show the parabolic behaviour of the equation of state, and that the parametrized ReaxFF can reproduce the results from DFT within an acceptable margin of error for high densities of the crystals, but shows a degradation on low densities.
 As for the trends in stability of the three phases, ReaxFF is unable to properly reproduce it.
-The reported experimental trend places $\alpha$-La as the most stable, followed by $\gamma$-La, and then by$\beta$-La.
-In the case of ReaxFF the trend goes from most stable to less stable as $\gamma$-La, $\beta$-La, and $\alpha$-La.
+The reported experimental trend places $\alpha$-La as the most stable phase, followed by $\gamma$-La, and then by$\beta$-La.
+In the case of ReaxFF, the predicted most stable phase corresponds to that of the$\gamma$-La, followed by $\beta$-La, and placing $\alpha$-La as the least stable phase.
 While the inability to reproduce stability is a known issue in ReaxFF, it is worth mentioning that in the case of La, the differences in energy between the phases is in the order of $\approx$~0.5~kcal/mol.
@@
 
-The bulk modulus for $\alpha$-La was obtained by fitting the calculated points to the Birch-Murnaghan equation of state\cite{fu_first-principles_1983}, and the value obtained of 25.6\,GPa agrees with an approximate 8\% of error compared to the reported experimental bulk modulus value of 27.9\,GPa.\cite{lide2003crc}
+The bulk modulus for $\alpha$-La was obtained by fitting the calculated points close to the minimums to the Birch-Murnaghan equation of state\cite{fu_first-principles_1983}, and the value obtained of 25.6\,GPa agrees with an approximate 8\% of error compared to the reported experimental bulk modulus value of 27.9\,GPa for $\alpha$-La.\cite{lide2003crc}
+
+\subsection{Energies of Formation}
+
+For the Lanthanum oxides, and in general for any other metal or alloy compounds, the energy of formation is another important quantity that characterize the stability of their phases.
+The two phases parametrized in this work ... \emph{need to wait for results from update force field}
 
@@
 
-Given the differences, in structure and energetics, of the surface compared to the bulk, it is necessary to introduce this behaviour to the force field.
-To this end, slabs of various perovskites were constructed from their bulk counterparts to extend the ReaxFF force field.
-\textbf{Calculations currently going on}
+Given the differences, in structure and energetics, of the surface compared to the bulk, we introduce this quantity to the training of the force field to enable the description of segregation and interaction of the oxides with vacuum/air.
+To this end, slabs of the oxides were constructed from their bulk counterparts and the energy used for parametrization, $\Delta_f E_s$, was obtained using the following expression:
+\begin{equation}
+    \Delta_f E_s = \frac{1}{N_s}(E_{slab} - nE_{bulk}),
+\end{equation}
+where $N_s$ is the total number of surface atoms, $n$ the total number of repeated unit cells of the system, $E_{slab}$ the total energy of the slab system, and $E_{bulk}$ the total energy of the bulk unit cell.
 
@@
 
-Introduction of Ca in the A--site of the perovskites favours the formation of oxygen vacancies due to the change in ionic size compared to La and the different charges of these cations. \textbf{cite}
-Also, the formation of oxygen vacancies allow for ionic diffusion through the solid, which is an important process present when these solids are used as electrodes in solid oxide fuel or electrolysis cells.
-The existence of oxygen vacancies in the system needs to be captured by ReaxFF in the form of correctly capturing changes in the chemical environment and in the relative stability of the solid unit cell in the absence of one oxygen.
-For various perovskites, the oxygen vacancy formation energy is calculated and incorporated into the dataset used to fit ReaxFF.
+Presence of oxygen vacancies in the Lanthanum oxides allow for ionic diffusion of oxygen to occur through the solid.
+This process permits rearrangement of the crystalline structure of the solid and may be involved during the crystalline phase transition process of La$_2$O$_3$ \emph{confirm and add citation}.
+The existence of oxygen vacancies in the system is captured by ReaxFF by adding to the training set a systematic description of energetic variations due to the chemical environment of La, by adding the relative stability of the bulk and surface unit cell in the absence of different concentrations of oxygen.
+The first part was carried out by adding the relative energy differences between the series of (La$_2$O$_3$)$_n$ clusters, with $n$ going from 1 to 9.
+The second part involved calculation of oxygen vacancy formation energies for La$_2$O$_3$
+
+\emph{need to add results}
 
@@
 
-\subsection{Nanoparticle formation of La$_2$O$_3$}
+\subsection{Phase transitions of La}
 
-\subsection{Oxygen Diffusion through the Perovskites}
+As mentioned before, depending on the temperature, La can be found in three different crystal structures.
+We use the parameters obtained from our parametrization to show if ReaxFF is capable of capturing these features.
 
-To exemplify the dynamics on the bulk, diffusion of O$_2^{-2}$ is followed through the perovskite in bulk phase.
-Also, to account for the accuracy of the force field, the expansion coefficient is computed for LCFCr and this value is compared to experimental results.
+\subsection{Phase transitions of La$_2$O$_3$}
 
-\subsection{CO$_2$ Interactions on the Surface}
+Lanthanum oxide only exists as one stable form, hexagonal packed, at ambient temperatures.
+Studies at high temperature using x-ray diffraction and neutron diffraction have showed that at in the range of 2313 and 2383 K Lanthanum oxide transforms to partially ordered hexagonal and then to cubic \emph{link references}.
+The enthalpies of transition between these structures have been estimated to be in the order of 10--15 kcal/mol by applying the van't Hoff equation to the ZrO$_2$--La$_2$O$_3$ and phase diagram and by comparison to the Y$_2$O$_3$ transition from cubic to hexagonal structure.
+\emph{link references}
 
-\textbf{this may be ommited for a future paper}
-
-Using a slab of a representative portion \textbf{fill in details of the real size} of the surface of the LCFCr, various mixtures of gases are fed into one of the surfaces ...
-
-Formation of intermediates is observed at 1073 K \textbf{double check temperature}
+We apply our developed ReaxFF parameters to capture the temperature at which these transitions occurs.
 
@@
 \centering
-\includegraphics[width=\textwidth]{three-La-eos.pdf}
+\includegraphics[scale=1]{three-La-eos.pdf}
 \caption{Calculated equations of state corresponding to crystalline La in hexagonal (top), fcc (middle), and bcc (bottom) forms.}
@@
 
+\begin{figure}[hbtp]
+\centering
+\includegraphics[scale=0.75]{Paper/images/La-nvt-EvsT.png}
+\caption{Equation of state of La. Three distinct changes in slope at 550 and 1134 K indicate changes into a different crystalline structure.}
+\label{fig:la-nvt-EvsT}
+\end{figure}
+
+\pagebreak
+
+\begin{figure}[hbtp]
+\centering
+\includegraphics[scale=0.75]{Paper/images/La2O3-VvsT.png}
+\caption{Equation of state of La$_2$O$_3$. According to estimated data, changes in volume at 2313 and 2383 K correspond to the changes in the crystalline structure of Lanthanum oxide.}
+\label{fig:la2O3-npt-VvsT}
+\end{figure}
+
+\pagebreak
 \bibliography{co2perov2}

### 2019-08-20 Paper/paper.tex
Updates from Overleaf
fixed typos

@@
 
-The parametrization of the force field was performed using various stages, and it started with known parameters for C, H, O, S, Fe, and Cr from a previous study of hydrocarbon oxidation on pyrite--covered Cr$_2$O$_3$; \cite{shin_development_2015} and for Ca from a previous study of calcium oxyde hydration.
+The parametrization of the force field was performed using various stages, and it started with known parameters for C, H, O, S, Fe, and Cr from a previous study of hydrocarbon oxidation on pyrite--covered Cr$_2$O$_3$; \cite{shin_development_2015} and for Ca from a previous study of calcium oxide hydration.
 \cite{manzano_hydration_2012}
@@
 \centering
-\includegraphics[scale=1]{three-La-eos.pdf}
+\includegraphics[scale=0.5]{Paper/images/LaEoS.png}
 \caption{Calculated equations of state corresponding to crystalline La in hexagonal (top), fcc (middle), and bcc (bottom) forms.}

### 2019-12-12 Paper/paper.tex
Added more info to introduction and details on other sections

@@
 \usepackage{epstopdf}
-\usepackage{natbib}
+\usepackage[numbers]{natbib}
 
@@
 \begin{abstract}
-\textbf{abstract needs to be updated to reflect last changes}
+\textbf{abstract needs to be updated to reflect changes in focus of the paper}
 
@@
 We describe the procedure followed and provide results that validate the derived parameters in their ability to describe bulk structures, surfaces, and nanoparticles.
-Comparison of our results using ReaxFF and electronic structure methods show good agreement in the reproduction of surfaces energies and bulk modulus; with the latter showing good agreement with experimentally reported results.
-We also show that our parametrization is able to capture the trend in adsorption energies between Lanthanum oxides and adsorbates like methane and water \textbf{to be obtained}.
-These results highlight the utility of ReaxFF to study systems containing Lanthanum and provide a significant addition to reactive molecular dynamics for studying properties and even redox properties on Lanthanum oxide surfaces.
+Comparison of our results using ReaxFF and electronic structure methods show good agreement in the reproduction of surfaces energies and bulk modulus, as well as good agreement with experimentally reported results for the latter.
+We also show that the resulting force field can capture changes in the crystal structure of Lanthanum and its oxides by reproducing the expected crystal structure at various ranges of temperature as well as reasonable values for the temperatures in which crystal structure phase transitions occurs.
+Overall, these results highlight the utility of ReaxFF to study systems containing Lanthanum and its power to predict thermodynamic related processes involving the crystal structure of the system.
 
@@
 Particularly, catalysts based on Lanthanum oxide have shown a good efficiency in the oxidative coupling of methane to form ethane and/or ethylene \textbf{import citation}, or as main components of electro--catalysts used in CO$_2$ conversion to CO \textbf{import citation}.
+While the experimental properties of Lanthanum and its oxides are well studied and known \textbf{import citation}, their interaction with other compounds is an area of growing study and interest for advancements in material design involving Lanthanum.
 
-% what is the problem with lanthanum
-\emph{need to introduce more about uses of La}
+%\emph{need to introduce more about uses of La}
 
-Quantum mechanical calculations have been carried out to understand the role and influence, if any, of Lanthanum on its many applications.
-However, many of the phenomena that takes place in catalysis involve the interaction of many atoms for which rigorous quantum mechanical calculations are unfeasible.
-For this reason, force fields are commonly used to study applications via molecular dynamics calculations.
-In particular, the behaviour of La$^3+$ in aqueous solution has been studied by various groups using different parametrization strategies to improve the accuracy of the description of the interaction between Lanthanum and water \cite{duvail2007pair}.
-These approaches have proven to successfully describe the La--O interaction in liquid water, but due to the size of Lanthanum the introduction of some form of explicit polarizability is necessary to properly describe the interactions between Lanthanum and other elements.
+Computational methods are often used together with experimental data to study interaction between atoms and gain an understanding of them.
+Quantum mechanical calculations are one of the most used computational methods to resolve the interaction between all electrons and atomic nuclei of a system and are based in solving the Schrödinger equation of a particular system.
+However, many of the phenomena of interest involving La, and material design in general, take place between many atoms, making rigorous quantum mechanical calculations unfeasible when many atoms are present in the system.
+Alternatively, force fields can be used instead of quantum mechanical calculations when the size of the system makes the latter computationally prohibitive.
+Most force fields use parametrized potential energy functions to capture the interaction between atoms of a system and reproduce, to some extent, its high dimensional potential energy surface.
+Because these functions are easier to evaluate than their quantum mechanical counterparts, it is possible to model systems of many atoms and capture the dynamics on nanosecond time scales.
+At the same time, the major drawback of using force fields is the loss of the accurate quantum mechanical interaction between particles, which is important in Lanthanum due to the complexity introduced by strongly correlated 4f electrons and the high polarizability of the atom.
+For this reason, it is critical to have good quality force fields that can reproduce the properties of Lanthanum and its oxides and expand them to study their interactions with other compounds.
 
-One of the major drawbacks of the use of general polarizable force fields is the impossibility to describe chemical reactions, as these models disable explicit bond breaking and formation to produce transferable parameters and simple expressions for calculating energies and forces.
-But, with the increasing computational power processing, reactive force fields that can capture bond breaking and formation on--the--fly have been developed actively during the last decade.
-Particularly, ReaxFF is a reactive force field that has been extensively used to study successfully reactive events between solid, liquid, and gas phases.
-This transferability between phases, and the possibility to study phenomena where chemical events and dynamical factors are of importance makes ReaxFF a powerful tool that bridges the lower computational expense from force fields and the quantum mechanical description of a system.
-Although the current form of ReaxFF has been in development since 2008 \cite{chenoweth_reaxff_2008} and many elements have been parametrized to be used in ReaxFF not all interactions have been fully parametrized, and some elements still remain to be parametrized.
-An important point is that parameters used in ReaxFF are heavily dependent on the applications for which they have been explicitly parametrized, so while some parameters can be transferable testing is necessary to ensure that interactions are well described.
+Modeling of Lanthanum has been commonly done with general force fields, being UFF the most used \textbf{import citation}, but using this approach has some shortcomings.
+General force fields favor transferability and simplicity, an approach that has been very successful for elements in the first rows of the periodic table, but in the case of heavier elements this approach is not enough to capture their behaviour, and specialized force fields need to be developed to improve on the shortcomings of the general force fields.
+In particular for La, the behaviour of La$^{3+}$ in aqueous solution is the most studied interaction and has been investigated by various groups using different parametrization strategies \cite{clavaguera2005molecular,duvail2007pair}.
+These studies highlight the importance of introducing some form of explicit polarizability and many-body effects to improve the accuracy of the Lanthanum--water interaction.
 
-The purpose of this study is to generate a set of parameters for Lanthanum and Lanthanum Oxide that can be used for describing solid state materials used in catalysis and as a base for further development in applications that involve interactions with CO$_2$ or H$_2$O to name a couple.
-To this end, in the remainder of this paper, we introduce ReaxFF and a parametrization strategy in Sec.~\ref{sec:reaxff-strategy}; the computational methods used, i.e.
-electronic structure calculations in Sec.~\ref{sec:dft-details}; and molecular dynamics simulations in Sec.~\ref{sec:md-details}.
-Then, we discuss in Sec.~\ref{sec:results-and-discussion} the quality of the newly generated parameters by analyzing the ability of the ReaxFF to reproduce the generated dataset from quantum mechanical calculations.
-Finally, we use the parameters obtained to model some possible applications discuss the results in Sec.~\ref{sec:applications}, and present our concluding remarks in Sec.~\ref{sec:conclusions}
+Another shortcoming of general force fields is the impossibility to describe chemical reactions, which would require modeling explicit bond breaking and formation, historically handled only by quantum mechanical calculations.
+However, development of computational techniques and increasing computational power have given rise to the use of reactive force fields \cite{meuwly2019reactive}, where bond breaking and formation is treated by introducing functions describing changes in the bond order of the atoms \textbf{import citation}, or by using valence bond theory \textbf{import citation}, or by explicitly computing the potential energy surface of the system on--the--fly \textbf{import citation}.
+Most of these methods are novel, and those involving the computation of the potential energy surface of the system on--the--fly still require a lot of computational resources.
+Nonetheless, among these methods ReaxFF \cite{van2001reaxff,chenoweth_reaxff_2008} is a reactive force field that has been used successfully to study reactive events in hydrocarbons \cite{van2001reaxff}, thermal decomposition of zinc-oxide \cite{russo2011atomistic}, H$_2$ on platinum surfaces, oxidation on aluminum surfaces \cite{ludwig2006dynamics}, and hydration on calcium oxide surfaces \cite{manzano_hydration_2012}, just to mention some examples.
+ReaxFF is a promising reactive force field, it has room for performance improvements and can be extended to study a wide range of chemical reactions and phenomena \cite{senftle_reaxff_2016}.
+
+The formalism used to develop ReaxFF gives it the ability to describe not only chemical reactions but also interactions between different phases, e.g.
+solid--liquid, gas--solid, etc.
+as evidenced by some of the studies cited previously.
+In addition, due to the many functions used to capture the interactions between atoms in ReaxFF, some form of polarizability is present in the force field, as well as many-body effects.
+For these reasons, ReaxFF is a viable force field for studying phenomena involving crystal structure determination and chemical reactions (e.g. heterogeneous catalysis) of Lanthanum.
+
+Although the current form of ReaxFF has been in development since 2008 \cite{chenoweth_reaxff_2008} and many elements have been parametrized to be used in ReaxFF, transferability between parameters is limited.
+Also, because ReaxFF does not build on the concept of atom types, fitting to reference data is somewhat necessary.
+For systems containing atoms that are commonly studied, e.g. C, H, O, etc. fitting may be minimal compared to systems where one atom has no previous known parametrization, which is the case for La.
+
+The purpose of this study is to generate a set of parameters for Lanthanum and Lanthanum oxide that can be used for describing their thermodynamic and structural properties, and serve as a base for further development in applications that involve interactions with other materials.
+To this end, in the remainder of this paper, we introduce the mathematical form of ReaxFF and a parametrization strategy in Sec.~\ref{sec:reaxff-strategy}; the computational methods used, i.e.
+electronic structure calculations in Sec.~\ref{sec:dft-details}, and molecular dynamics simulations in Sec.~\ref{sec:md-details}.
+Then, we discuss in Sec.~\ref{sec:results-and-discussion} the quality of the newly generated parameters by analyzing the ability of ReaxFF to reproduce a dataset from quantum mechanical calculations.
+In the following section Sec.~\ref{sec:applications}, we use the parameters obtained to predict some structural and thermodynamic properties and discuss the results, and we present our concluding remarks in Sec.~\ref{sec:conclusions}
 
@@
 ReaxFF is a force field based on the dynamical computation of the bond-order, which dictates the connectivity between atoms on the fly.
-This approach allows ReaxFF to consider bond breaking and formation, and therefore permits to follow the apparition of intermediates.
+This approach allows ReaxFF to consider bond breaking and formation, and follow the apparition of intermediates during a chemical reaction.
 In complex systems this ability proves to be invaluable for following reaction mechanism when the number of atoms are in the order of thousands or higher.\cite{migliorati_development_2017,merinov_reaxff_2014,
@@
 liu_reaxff-lg:_2011}
-This way, ReaxFF bridges classical molecular dynamics and quantum--mechanical approaches while avoiding exponential scaling of calculation times.
+
+To this end, ReaxFF uses the following energy terms:
+\begin{equation}
+E = E_{bond} + E_{over} + E_{angle} + E_{tors} + E_{vdW} + E_{coul} + E_{special},
+\end{equation}
+where $E_{bond}$ is the energy associated with bond formation between atoms and it is function of the bond order; $E_{angle}$ and $E_{torsion}$ are the three-body angle and four-body torsion strains, respectively, which are also dependent of the bond order; $E_{over}$ is an energy penalty that prevents overcoordination of atoms based on atomic valence rules; $E_{coul}$ and $E_{vdW}$ are the coulombic and van der Waals interactions, respectively; and $E_{special}$ are less commonly used energy terms that are used to describe specific properties like lone-pair interactions, conjugation, $C_2$ corrections, hydrogen binding and undercoordination.
+For an introduction of the full mathematical form of the various energy terms as well as their parameters refer to the publications from \citet{van2001reaxff} and \citet{chenoweth_reaxff_2008}.
 
@@
 \end{equation}
-Where $x_{i}$ is the value of a property $x$ (e.g.
-heat of formation, geometries, energetic differences, etc.); $x_{ReaxFF,i}$ is such property calculated using ReaxFF; and $w_i$ is the weight, or accuracy, associated to the desired deviation between both $x_i$ and $x_{ReaxFF,i}$
-In this work the Monte Carlo Force Field Optimizer,\cite{iype_parameterization_2013} part of the ADF package, has been used to fit the various parameters of the force field, mostly because the method has been shown to give good results independent of the initial guess for the force fields parameters.
+Where $x_{i}$ is the reference value of a property $x$ (e.g.
+heat of formation, bond distances, angles, charges, energetic differences, etc.); $x_{ReaxFF,i}$ is the property calculated using ReaxFF; and $w_i$ is a weight, or accuracy, associated to the desired deviation that can be tolerated between both $x_i$ and $x_{ReaxFF,i}$.
+In this work the error function minimization is carried out using the CMA-ES force-field optimizer,\textbf{fix citations}\cite{iype_parameterization_2013} part of the ADF package.
+Among various methods for parametrizing ReaxFF, CMA-ES has shown to give reliable results independent of the initial guess for the force fields parameters, which in this work is of concern as full parameters for La has not been generated yet.
 
-The parametrization of the force field was performed using various stages, and it started with known parameters for C, H, O, S, Fe, and Cr from a previous study of hydrocarbon oxidation on pyrite--covered Cr$_2$O$_3$; \cite{shin_development_2015} and for Ca from a previous study of calcium oxide hydration.
-\cite{manzano_hydration_2012}
-
-With starting parameters for most elements except for Lanthanum, the first stage of the parametrization involved fitting the La--La parameters of the force field to the following: quantum mechanically calculated equations of state corresponding to three solid phases of La, i.e.
-double hexagonal close packed (dhcp, $\alpha$-La), face centered cubic (fcc, $\gamma$-La), and body centered cubic (bcc, $\beta$-La); and data from the electronic structure calculation of the La$_2$ molecule was added.
-This stage was carried out while keeping parameters for other interactions unchanged.
+The parametrization of the force field was performed using various stages.
+The first stage of the parametrization involved fitting the La--La parameters of the force field to the following: quantum mechanically calculated equations of state corresponding to three solid phases of La, i.e.
+double hexagonal close packed (dhcp, $\alpha$-La), face centered cubic (fcc, $\gamma$-La), and body centered cubic (bcc, $\beta$-La); data from the electronic structure calculation of the La$_2$ and La$_3$ molecules were added as well.
+At this point, the starting parameters (initial conditions) for La were randomly generated, and various fittings were carried out with different initial conditions
 The following stage involved further fitting of the La--La parameters, namely those related to the electrostatic interaction (EEM shielding, EEM electronegativity, and EMM hardness), and the La--O parameters by adding to the dataset Mulliken charges and geometrical information obtained from the optimized structures of the La$_2$O$_3$ cluster, three La$_4$O$_6$ clusters, and one La$_6$O$_9$ cluster.
 Also, the equations of state corresponding to two solid structures of La$_2$O$_3$ were computed and added.
+In this stage, the La--La parameters obtained from the first stage were kept fixed, and the initial conditions of stage two corresponded to a set of force fields parameters that had the lowest values for the error function in stage one.
+As a last stage, all parameters were allowed to vary during the fitting procedure, using as initial conditions the force field parameters that had the lowest values for the error function in stage two.
+The best force field for which results are presented in the following sections was the one with the lowest error function value and, also, presenting the lowest error function value for a validation dataset.
+The datasets were constructed such that all the quantum mechanical properties calculated were distributed in a 9:1 ratio to form the training and validation datasets.
 
@@
 DFT calculations are carried out using Quantum Espresso,\cite{giannozzi_advanced_2017} for all solid structures in bulk or slab form.
-These calculations were performed using the pseudo--potentials from the PSlibrary including scalar-relativistic effects due to the presence of Lanthanum \textbf{put references}.
+These calculations were performed using the pseudo--potentials from the PSlibrary including scalar-relativistic effects for Lanthanum \textbf{put references}.
 A value of 75.0 Ry was used for the kinetic energy cutoff, which was tested for convergence ensuring that $\Delta E_{tot} / \Delta E_{cut} <$ 0.01 eV was obtained per atom.
@@
 The criterion used involved using a k-point grid of 4 on the edge of a cell between 5 and 8 \AA in length, then to preserve the grid on bigger or smaller cells, the grid was scaled accordingly.
-The k-point grids used were also tested using the same criterion from energy converge to ensure convergence with respect to grid size.
+The k-point grids used were also tested using the same criterion from energy convergence to ensure convergence with respect to grid size.
 
-Because the transition metals present localized electronic density on their d--orbitals with strong correlation, the Hubbard correction is employed to take into account these effects.\textbf{put references}
-Values used for the Hubbard term, U, were taken from \textbf{put values, and justify about not determining their values from linear response theory}
+%Because the transition metals present localized electronic density on their d--orbitals with strong correlation, the Hubbard correction is employed to take into account these effects.\textbf{put references}
+%Values used for the Hubbard term, U, were taken from \textbf{put values, and justify about not determining their values from linear response theory}
 
@@
 using weights of 0.1 to 1.0.
-Because the relationship between energy and volume in solids allows to capture the stability of the phase, fitting of these curves give ReaxFF the ability to model accurately the bulk phase of the crystal structures for which it has been explicitly trained.
+Because the relationship between energy and volume in solids allows to capture the stability of the phase, fitting of these curves give ReaxFF the ability to model accurately the bulk phase of the crystal structures.
 
@@
 The equations of state for the three forms of Lanthanum are presented in Fig.~\ref{fig:laeos}.
-The plots show the parabolic behaviour of the equation of state, and that the parametrized ReaxFF can reproduce the results from DFT within an acceptable margin of error for high densities of the crystals, but shows a degradation on low densities.
+The plots show the parabolic behaviour of the equation of state, and that the parametrized ReaxFF can reproduce the results from DFT within an acceptable margin of error for high densities of the crystals, but shows a degradation when volume is increased (low densities), particularly for $\beta$-La.
 As for the trends in stability of the three phases, ReaxFF is unable to properly reproduce it.
-The reported experimental trend places $\alpha$-La as the most stable phase, followed by $\gamma$-La, and then by$\beta$-La.
-In the case of ReaxFF, the predicted most stable phase corresponds to that of the$\gamma$-La, followed by $\beta$-La, and placing $\alpha$-La as the least stable phase.
-While the inability to reproduce stability is a known issue in ReaxFF, it is worth mentioning that in the case of La, the differences in energy between the phases is in the order of $\approx$~0.5~kcal/mol.
+The reported experimental trend places $\alpha$-La as the most stable phase, followed by $\beta$-La, and then by $\gamma$-La.
+In the case of ReaxFF, the predicted most stable phase corresponds to that of the $\gamma$-La, followed by $\beta$-La, and placing $\alpha$-La as the least stable phase.
+While the inability to reproduce the relative stability of two different phases is a known issue in ReaxFF, it is worth mentioning that in the case of La, the differences in energy between the phases is in the order of less than $\approx$~5~kcal/mol.
 It is then unsurprising that the parametrized force field is unable to exactly reproduce the trend,  given how small the difference in energy is compared to the target error in the fitting of the force field, which averages around 5~kcal/mol.
@@
 
-\subsection{Energies of Formation}
-
-For the Lanthanum oxides, and in general for any other metal or alloy compounds, the energy of formation is another important quantity that characterize the stability of their phases.
-The two phases parametrized in this work ... \emph{need to wait for results from update force field}
-
 \subsection{Surface Energies}
 
-Given the differences, in structure and energetics, of the surface compared to the bulk, we introduce this quantity to the training of the force field to enable the description of segregation and interaction of the oxides with vacuum/air.
+Given the differences, in structure and energetic, of the surface compared to the bulk, we introduce this quantity to the training dataset to enable the description of segregation and interaction of La and its oxides with vacuum/air.
 To this end, slabs of the oxides were constructed from their bulk counterparts and the energy used for parametrization, $\Delta_f E_s$, was obtained using the following expression:
@@
 Presence of oxygen vacancies in the Lanthanum oxides allow for ionic diffusion of oxygen to occur through the solid.
-This process permits rearrangement of the crystalline structure of the solid and may be involved during the crystalline phase transition process of La$_2$O$_3$ \emph{confirm and add citation}.
-The existence of oxygen vacancies in the system is captured by ReaxFF by adding to the training set a systematic description of energetic variations due to the chemical environment of La, by adding the relative stability of the bulk and surface unit cell in the absence of different concentrations of oxygen.
-The first part was carried out by adding the relative energy differences between the series of (La$_2$O$_3$)$_n$ clusters, with $n$ going from 1 to 9.
-The second part involved calculation of oxygen vacancy formation energies for La$_2$O$_3$
+This process permits rearrangement of the crystalline structure of the solid and may be an important step during the crystalline phase transition process of La$_2$O$_3$ \emph{confirm and add citation}.
+The existence of oxygen vacancies in the system is captured by ReaxFF by adding to the training set a systematic description of energetic variations due to the chemical environment of La, and by adding the relative stability of bulk and surfaces at different oxygen vacancy concentrations.
+The first part was carried out by adding the relative energy differences between the series of La$^{3+}$--(OH$_2$)$_n$ clusters, with $n$ going from 1 to 9 Fig.~\ref{fig:LaOH2clusters}.
+The second part involved adding values calculated for oxygen vacancy formation energies of La$_2$O$_3$ in bulk and in the surface of a slab.
+The value corresponding to the oxygen vacancy formation energy was introduced into the dataset according to the following expression:
+\begin{equation}
+    \Delta E = E_{system} - E_{nO} - \frac{1}{2}nE_{O_2},
+\end{equation}
+where $E_{system}$ corresponds to the energy of the bulk or surface with no vacancies; $E_{nO}$ is the energy of the bulk or surface with $n$ atoms of oxygen removed; and $E_{O_2}$ is the energy of a molecule of O$_2$ in gas phase.
 
-\emph{need to add results}
+\emph{need to add results. A table containing all energy data with a column being DFT and the other ReaxFF is an option}
 
@@
 
-As mentioned before, depending on the temperature, La can be found in three different crystal structures.
-We use the parameters obtained from our parametrization to show if ReaxFF is capable of capturing these features.
+La can be found in three different crystal structures depending on the temperature.
+At low temperatures (<277ºC) the stable modification of lanthanum is $\alpha$-La (hexagonal with a = 0.3772 nm, c = 1.2144 nm).
+In the range 277º to 861ºC, $\beta$-La with cubic lattice (a = 0.5296 nm) becomes more stable with a density of 6.19 g/cm$^3$.
+Within the 861º to 920ºC range, the most stable modification is $\gamma$-La with an fcc lattice of $\alpha$-Fe type (a = 0.426 nm) and a density of 5.97 g/cm$^3$.
+We use the parameters obtained from our parametrization to show if ReaxFF is capable of capturing the first crystal phase transition.
 
@@
 \emph{link references}
-
-We apply our developed ReaxFF parameters to capture the temperature at which these transitions occurs.
+We apply our developed ReaxFF parameters to show if they are capable of capturing the temperature at the transitions from hexagonal to cubic occurs.
 
@@
 \pagebreak
+
+\begin{figure}[hbtp]
+\centering
+\includegraphics[scale=0.75]{Paper/images/placeholder.png}
+\caption{La$^{3+}$--(OH$_2$)$_n$ clusters. Some bond distances obtained via DFT are highlighted and the values obtained from ReaxFF are presented in parethesis.}
+\label{fig:LaOH2clusters}
+\end{figure}
+
+\pagebreak
+
+\begin{figure}[hbtp]
+\centering
+\includegraphics[scale=0.75]{Paper/images/placeholder.png}
+\caption{Snapshot showing La crystal structure at a temperature where (a) the packed hexagonal structure is predominant, and (b) the fcc structure is predominant.
+(c) Radial distribution functions showing the differences between the packed hexagonal and fcc structure of La}
+\label{fig:La-alpha-gamma-RDF}
+\end{figure}
+
+\pagebreak
+
+\begin{figure}[hbtp]
+\centering
+\includegraphics[scale=0.75]{Paper/images/placeholder.png}
+\caption{Evolution of the radial distribution function from packed hexagonal to fcc structure with respect to temperature for La}
+\label{fig:LaRDFevolution}
+\end{figure}
+
+\pagebreak
+
+\begin{figure}[hbtp]
+\centering
+\includegraphics[scale=0.75]{Paper/images/placeholder.png}
+\caption{Snapshot showing La$_2$O$_3$ crystal structure at a temperature where (a) the cubic, and (b) the hexagonal structure is predominant.
+(c) Radial distribution functions showing the differences between the two diffent structures of the La$_2$O$_3$ crystal}
+\label{fig:La2O3-A-C-RDF}
+\end{figure}
+
+\pagebreak
+
+\begin{figure}[hbtp]
+\centering
+\includegraphics[scale=0.75]{Paper/images/placeholder.png}
+\caption{Evolution of the radial distribution function from hexagonal to cubic structure with respect to temperature for La$_2$O$_3$}
+\label{fig:La2O3RDFevolution}
+\end{figure}
+
+\pagebreak
 \bibliography{co2perov2}
